waRne - Putting cricket analytics in a spin

### 2020-10-03 waRne paper.Rmd
push
push

---
title: "waRne - Putting cricket analytics in a spin"
authors: "unknown 1", "unknown 2"
output:
  pdf_document:
    toc: no
  html_document:
    toc: yes
    toc_float: yes
    keep_md: yes
  word_document:
    toc: yes
bibliography: references.bib
---

>>>>

---
title: "waRne - Putting cricket analytics in a spin"
authors: unknown1, unknown2
output:
  pdf_document:
    toc: no
  html_document:
    toc: yes
    toc_float: yes
    keep_md: yes
  word_document:
    toc: yes
bibliography: references.bib
---
